\documentclass[11pt,a4paper]{article}
\pdfoutput=1
\usepackage{jinstpub}         
%\usepackage{Styles/jinstpub} %%%% Comment previous line and comment uncomment this line if using pdflatex from terminal



\newif\ifshowcomments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% TO HIDE COMMENTS, FOLLOWING LINE SHOULD BE \showcommentsfalse, 
%%% OTHERWISE \showcommentstrue
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\showcommentstrue
\ifshowcomments
\newcommand{\CD}[1]{\textcolor{purple}{CD: #1}}
\newcommand{\BS}[1]{\textcolor{blue}{BS: #1}}
\else
\newcommand{\CD}[1]{}
\newcommand{\BS}[1]{}
\fi 

\usepackage[colorinlistoftodos]{todonotes}


\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{lineno}
%\linenumbers

\usepackage{titlesec}
\titleformat{\paragraph}[runin]
{\bfseries\scshape}{\theparagraph}{1em}{}
\setcitestyle{square}

\input{symbols.tex}

\date{\today}

\title{\icemc: A Monte Carlo Simulation for Cosmogenic Neutrinos interacting in the Antarctic ice as viewed by the Antarctic Impulsive Transient Antenna (ANITA)}

\collaboration{ANITA Collaboration}


\affiliation[uc]{Dept. of Physics, Enrico Fermi Inst., Kavli Inst. for Cosmological Physics, Univ. of Chicago , Chicago, IL 60637.}
\affiliation[ucla]{Dept. of Physics and Astronomy, Univ. of California, Los Angeles, Los Angeles, CA 90095.}
\affiliation[osu]{Dept. of Physics, Center for Cosmology and Particle Astrophysics, Ohio State Univ., Columbus, OH 43210.}
\affiliation[uh]{Dept. of Physics and Astronomy, Univ. of Hawaii, Manoa, HI 96822.}
\affiliation[ntu]{Dept. of Physics, Grad. Inst. of Astrophys.,\& Leung Center for Cosmology and Particle Astrophysics, National Taiwan University, Taipei, Taiwan.}
\affiliation[ku]{Dept. of Physics and Astronomy, Univ. of Kansas, Lawrence, KS 66045.}
\affiliation[mephi]{National Research Nuclear University, Moscow Engineering Physics Institute, 31 Kashirskoye Highway, Russia 115409.}
\affiliation[wu]{Dept. of Physics and McDonnell Center for the Space Sciences, Washington Univ. in St. Louis, MO 63130.}
\affiliation[slac]{SLAC National Accelerator Laboratory, Menlo Park, CA, 94025.}
\affiliation[ud]{Dept. of Physics, Univ. of Delaware, Newark, DE 19716.}
\affiliation[ucl]{Dept. of Physics and Astronomy, University College London, London, United Kingdom.}
\affiliation[jpl]{Jet Propulsion Laboratory, Pasadena, CA 91109.}
\affiliation[ccap]{Center for Cosmology and Particle Astrophysics, Ohio State Univ., Columbus, OH 43210.}
\affiliation[calpoly]{Physics Dept., California Polytechnic State Univ., San Luis Obispo, CA 93407.}
\affiliation[mpl]{Max-Planck-Institut f\"{u}r Kernphysik, 69117 Heidelberg, Germany.}
\affiliation[brus]{Astrophysical Institute, Vrije Universiteit Brussel, Pleinlaan 2, 1050, Brussels, Belgium.}
\affiliation[lsst]{LSST, 950 North Cherry Avenue, Tucson, AZ 85721}
\affiliation[ucsd]{Center for Astrophysics and Space Sciences, Univ. of California, San Diego, La Jolla, CA 92093}


\author[osu]{P.~Allison}
\author[osu]{O.~Banerjee}
\author[ucl]{L.~Batten} 
\author[osu]{J.~J.~Beatty} 
\author[uc,lsst]{K.~Bechtol}
\author[jpl]{K.~Belov}
\author[ku,mephi]{D.~Z.~Besson}
\author[wu]{W.~R.~Binns} 
\author[wu]{V.~Bugaev} 
\author[ud]{P.~Cao} 
\author[ntu]{C.~C.~Chen} 
\author[ntu]{C.~H.~Chen}
\author[ntu]{P.~Chen} 
\author[ud]{J.~M.~Clem} 
\author[osu]{A.~Connolly} 
\author[ucl]{L.~Cremonesi} 
\author[osu]{B.~Dailey} 
\author[uc]{C.~Deaconu} 
\author[wu]{P.~F.~Dowkontt} 
\author[uh]{B.~D.~Fox} 
\author[osu]{J.~W.~H.~Gordon}
\author[uh]{P.~W.~Gorham} 
\author[uh]{B.~Hill} 
\author[ntu]{J.~J.~Huang}
\author[osu]{R.~Hupe} 
\author[wu]{M.~H.~Israel} 
\author[jpl]{K.~M.~Liewer}
\author[ntu]{S.~Y.~Lin}
\author[ntu]{T.~C.~Liu} 
\author[uc]{A.~Ludwig} 
\author[uh]{L.~Macchiarulo} 
\author[uh]{S.~Matsuno} 
\author[osu]{K.~McBride}
\author[uh]{C.~Miki} 
\author[ud,brus]{K.~Mulrey}
\author[ntu]{J.~Nam}
\author[ucl]{R.~J.~Nichol}
\author[ku,mephi]{A.~Novikov} 
\author[uc]{E.~Oberla} 
\author[osu]{S.~Prohira}
\author[wu]{B.~F.~Rauch}
\author[uh,ucsd]{J.~M.~Roberts}
\author[jpl]{A.~Romero-Wolf}
\author[uh]{B.~Rotter}
\author[uh]{J.~W.~Russell} 
\author[ucla]{D.~Saltzberg}
\author[ud]{D.~Seckel}
\author[uh,mpl]{H.~Schoorlemmer}
\author[ntu]{J.~Shiao}
\author[osu]{S.~Stafford}
\author[ku]{J.~Stockham}
\author[ku]{M.~Stockham}
\author[ucla]{B.~Strutt} 
\author[calpoly]{J.~Stuhr}
\author[uh]{G.~S.~Varner}
\author[uc]{A.~G.~Vieregg}
\author[ntu]{S.~H.~Wang}
\author[calpoly]{S.~A.~Wissel}


\abstract{A Monte Carlo simulation tool for the radio detection of Ultra High Energy (UHE) neutrino interactions in the Antarctic ice, \icemc, is described in this article.
This tool includes the simulation of UHE neutrinos, the parametrization of the Askaryan radiation generated by their interaction in the ice, the propagation of the radiation through ice and air to a simulated model of the third and fourth ANITA (Antarctic Impulsive Transient Antenna) flights.
This paper provides an overview of the \icemc simulation, a detailed description of the physics models used, data/simulation comparisons to validate the physics performance, and a summary of the impact of published results. Finally the sensitivity of the fourth ANITA flight is presented. If no neutrinos are detected, ANITA is expected to improve upon its world leading limit on the cosmogenic neutrino flux above $10^{19}$\,eV.}

\keywords{neutrino radio detection, ultra-high-energy, Monte Carlo}

\arxivnumber{...}

\begin{document}

\maketitle

\flushbottom

\input{1_introduction.tex}

\input{2_eventGeometry.tex}

\input{3_radioSignal.tex}

\input{4_propagationInIce.tex}

\input{5_ANITAinstrument.tex}

\input{6_validation.tex}

\input{7_sensitivity.tex}

\section{Acknowledgements}
\label{sec:ackowledgements}
We would like to thank the National Aeronautics and Space Administration and the National Science Foundation, especially the Office of Polar Programs.  We would especially like to thank the staff of the Columbia Scientific Balloon Facility and the logistical support staff enabling us to perform our work in Antarctica.  We are deeply indebted to those who dedicate their
careers to help make our science possible in such remote environments.
This work was supported by the Kavli Institute for Cosmological Physics at the University of Chicago.  Computing resources were provided by the University of Chicago Research Computing Center and the Ohio Supercomputing Center at The Ohio State University.
A. Connolly would like to thank the National Science Foundation
for their support through CAREER award 1255557. 
O. Banerjee and L. Cremonesi's work was also
supported by collaborative visits funded by the Cosmology and Astroparticle
Student and Postdoc Exchange Network (CASPEN).
The University College London group was also supported by the Leverhulme Trust. The Taiwan team is supported by Taiwan's Ministry of Science and Technology (MOST) under its Vanguard Program 106-2119-M-002-011.

\bibliographystyle{Styles/JHEP}
\renewcommand{\bibname}{References}
\bibliography{references.bib} 

\input{9_appendix.tex}




\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
